A meta analysis of tournaments and an evaluation of performance in the Iterated Prisoner's Dilemma.

### 2020-02-03 paper/main.tex
tweak abstract

\begin{abstract}
The Iterated Prisoner's Dilemma has been used for decades as a model of
behavioural interactions. From the celebrated performance of Tit for Tat, to the
introduction of the zero-determinant strategies, to the use of sophisticated
structures such as neural networks, the literature has been exploring the
performance of strategies in the game for years. The results of the literature,
however, have been relying on the performance of specific strategies in a finite
number of tournaments, whereas this manuscript evaluates
\numberofstrategies strategies' effectiveness in more than 40000 tournaments.
The top ranked strategies are presented, and moreover, the impact of features on
their success are analysed using machine learning techniques. The analysis
determines that the cooperating ratio of a
strategy in a given tournament compared to the mean and median cooperator is the
most important feature. The conclusions are distinct for different types of
tournaments. For instance a strategy with a theory of mind would aim to be the mean/median
cooperator in standard tournaments, whereas in tournaments with probabilistic
ending it would aim to cooperate 10\% of the times the median cooperator did.
\end{abstract}

>>>>

\begin{abstract}
The Iterated Prisoner's Dilemma has been used for decades as a model of
behavioural interactions. From the celebrated performance of Tit for Tat, to the
introduction of the zero-determinant strategies, to the use of sophisticated
structures such as neural networks, the literature has been exploring the
performance of strategies in the game for years. The results of the literature,
however, have been relying on a small number of somewhat arbitrarily selected
strategies in a very small number of tournaments,
casting doubt on the generalizability of results from statistical perspective.
This manuscript evaluates \numberofstrategies strategies in more than 40000
tournaments, presents the top performing strategies, and analyzes their
salient features.
The outcomes support that a strategy with a theory of mind should adjust it’s
cooperations based on the mean/median cooperator of its environment to be
successful; the adjustments are distinct for different tournament types.
\end{abstract}
